### 2019-07-01 README.Rmd
Added Formula 1 to README

In this step we will use the *pathEnrich* function to identify KEGG pathways that are enriched based on a list of genes we
are interested in and based on a list of background genes. This function may not always use the complete list of genes provided 
by the user. Specifically, it will only use the genes from the list provided that are also in
the most current species list pulled from the KEGG REST API using *get_kegg*, or from the older KEGG data loaded by the user from a 
previous *get_kegg* call. The *pathEnrich* function should be run at least twice, once for the genes of interest and once for the background.
Each *pathEnrich* call generates a dataframe summarizing the results of a traditional pathway enrichment analysis in which a Fisher's
Exact test is used to identify which KEGG pathways are enriched by the user's list of interesting genes with repect to background
enrichment.

>>>>

In this step we will use the *pathEnrich* function to identify KEGG pathways that are enriched (i.e. over-represented) based on a list of genes we
are interested in and based on a list of background genes. This function may not always use the complete list of genes provided 
by the user. Specifically, it will only use the genes from the list provided that are also in
the most current species list pulled from the KEGG REST API using *get_kegg*, or from the older KEGG data loaded by the user from a 
previous *get_kegg* call. The *pathEnrich* function should be run at least twice, once for the genes of interest and once for the background.
Each *pathEnrich* call generates a dataframe summarizing the results of an enrichment analysis in which a Fisher's
Exact test is used to identify which KEGG pathways are enriched by the user's list of interesting genes with repect to background
enrichment, and a p-value is calculated using a hypergeometric distribution (Formula 1). P-values are adjusted for multiple comparisons by controlling the False Discovery Rate (FDR) at 0.05.

$Formula 1:$

  $$P = 1-\sum_{i=0}^{k-1} \frac{\binom{m}{i}\binom{N-M}{n-i}}{\binom{N}{n}}$$
